Spatial variation of coronal Fourier power spectra

### 2016-08-01 tex/paper2/paper2.tex
paper edits, and Python 3 compliance
paper compiles

\section{Analysis}\label{sec:anal}
The data in each AIA channel are co-aligned to remove solar rotation
using the process as described in Appendix \ref{sec:app:data}.  The
result are a set of datacubes that show the same portion of the Sun
for the duration of the data.  The time-series of emission $I(t)$ from
a single pixel is apodized using the Hanning window, reducing ringing
effects in the \PS.  The full 12 second cadence is used, yielding time
series of 1800 samples.  The full spatial resolution is also retained
in order to obtain fine detail on the variation of frequency content
as a function of location.  This yields $???\times???=???$ spectra per
AIA channel for analysis.

@@

\acknowledgments

We are grateful to the developers of SSWIDL
\citep{1998SoPh..182..497F}, IPython \citep{ipython}, SunPy
\citep{mumford-proc-scipy-2013}, matplotlib
\citep{Hunter:2007} and the Scientific Python stack for providing data
preparation, manipulation, analysis and display packages.  This work
was supported by NASA award NNX13AE03G S01 funded through NASA ROSES
NNH12ZDA001N-SHP, and by a NSF Career grant 1255024 (JMA).

@@

\subsection{Estimating the power-law index in a power law power
  spectrum}\sec{sec:app:est}
Equation \ref{eqn:freqprob:all} describes the likelihood of the
observed Fourier power given a model for that power.  We assume that
the observed power law spectrum can be modeled by a simple power law
over all frequencies
\begin{equation}
S_{j} = Af_{j}^{-n}
\end{equation}
where $A$ is a constant, $f_{j}$ is the $j$'th Fourier frequency, and
$n$ is the power law index we wish to estimate.  An estimate can be
derived using Bayes' theorem. Using the likelihood function derived
above (\ref{eqn:freqprob:all}), and assuming the prior $p(A)\propto
A^{m}$ for some value of $m$, then 
\begin{equation}
p(n) \propto \int_{0}^{\infty} p(A) L dA.
\label{eqn:bayes}
\end{equation}
On integration,
\begin{equation}
\ln p(n) \propto n\sum_{j=1}^{N}\ln f_{j} - (N-m-1)\ln\left[\sum_{j=1}^{N}I_{j}f_{j}
\label{eqn:pnlog}
\end{equation}
For the purposes of this investigation, $m=0$ and an estimate to $n$
was found by finding calculating the value of $\ln p(n)$ in the range
$n=0\rightarrow4$ with steps of 0.01 and finding the value of $n$ that
maximized $\ln p(n)$.

@@

\begin{deluxetable}{cccccccc}
\tabletypesize{\scriptsize} \tablecolumns{5} \tablewidth{0pt}
\tablecaption{Acceptable parameter ranges and the fraction of model
  fits that exceed the parameter ranges.  Section \ref{sec:anal} describe the meaning of each parameter value\label{tab:acceptable}}
\tablehead{
  \multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Range} & \multicolumn{6}{c}{AIA channel}\\
  \colhead{ } & \colhead{ } & \colhead{94\AA} & \colhead{131\AA} & \colhead{171\AA} & \colhead{193\AA}  & \colhead{211\AA} & \colhead{335\AA} \\ }
\startdata 
$A$ & ???$\rightarrow$??? & 94 & 131 & 131 & 171 & 193 & 211 & 335 \\
$n$ & ???$\rightarrow$??? & 94 & 131 & 131 & 171 & 193 & 211 & 335 \\
$C$ & ???$\rightarrow$??? & 94 & 131 & 131 & 171 & 193 & 211 & 335 \\
$\alpha$ & ???$\rightarrow$??? & 94 & 131 & 131 & 171 & 193 & 211 & 335 \\
$\log_{10}(\beta)$ & ???$\rightarrow$??? & 94 & 131 & 131 & 171 & 193 & 211 & 335 \\
$\log_{10}(\delta)$ & ???$\rightarrow$??? & 94 & 131 & 131 & 171 & 193 & 211 & 335 \\
\enddata
%% Text for table notes should follow after the \enddata but before
%% the \end{deluxetable}. Make sure there is at least one \tablenotemark
%% in the table for each \tablenotetext.

>>>>

\section{Analysis}\label{sec:anal}
The data in each AIA channel are co-aligned to remove solar rotation
using the process as described in Appendix \ref{sec:app:data}.  The
result are a set of datacubes that show the same portion of the Sun
for the duration of the data.  The time-series of emission $I(t)$ from
a single pixel is apodized using the Hanning window, reducing ringing
effects in the \PS.  The full 12 second cadence is used, yielding time
series of 1800 samples.  The full spatial resolution is also retained
in order to obtain fine detail on the variation of frequency content
as a function of location.  This yields $333\times566=188478$ spectra
per AIA channel for analysis.

@@

\acknowledgments
We are grateful to the developers of SSWIDL
\citep{1998SoPh..182..497F}, IPython \citep{ipython}, SunPy
\citep{mumford-proc-scipy-2013}, matplotlib
\citep{Hunter:2007} and the Scientific Python stack for providing data
preparation, manipulation, analysis and display packages.  This work
was supported by NASA award NNX13AE03G S01 funded through NASA ROSES
NNH12ZDA001N-SHP, and by a NSF Career grant 1255024 (JMA).

@@

\subsection{Estimating the power-law index in a power law power spectrum}\label{sec:app:est}
Equation \ref{eqn:freqprob:all} describes the likelihood of the
observed Fourier power given a model for that power.  We assume that
the observed power law spectrum can be modeled by a simple power law
over all frequencies
\begin{equation}
S_{j} = Af_{j}^{-n}
\end{equation}
where $A$ is a constant, $f_{j}$ is the $j$'th Fourier frequency, and
$n$ is the power law index we wish to estimate.  An estimate can be
derived using Bayes' theorem. Using the likelihood function derived
above (\ref{eqn:freqprob:all}), and assuming the prior $p(A)\propto
A^{m}$ for some value of $m$, then 
\begin{equation}
p(n) \propto \int_{0}^{\infty} p(A) L dA.
\label{eqn:bayes}
\end{equation}
On integration,
\begin{equation}
\ln p(n) \propto n\sum_{j=1}^{N}\ln f_{j} - (N-m-1)\ln\left[\sum_{j=1}^{N}I_{j}f_{j}
\right]
\label{eqn:pnlog}
\end{equation}
For the purposes of this investigation, $m=0$ and an estimate to $n$
was found by finding calculating the value of $\ln p(n)$ in the range
$n=0\rightarrow4$ with steps of 0.01 and finding the value of $n$ that
maximized $\ln p(n)$.

@@

\begin{deluxetable}{cccccccc}
\tabletypesize{\scriptsize} \tablecolumns{8} \tablewidth{0pt}
\tablecaption{Acceptable parameter ranges and the fraction of model
  fits that exceed the parameter ranges.  Section \ref{sec:anal} describe the meaning of each parameter value\label{tab:acceptable}}
\tablehead{
  \multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Range} & \multicolumn{6}{c}{AIA channel}\\
  \colhead{ } & \colhead{ } & \colhead{94\AA} & \colhead{131\AA} & \colhead{171\AA} & \colhead{193\AA}  & \colhead{211\AA} & \colhead{335\AA} \\ }
\startdata 
$A$ & ???$\rightarrow$??? & 94 & 131 & 171 & 193 & 211 & 335 \\
$n$ & ???$\rightarrow$??? & 94 & 131 & 171 & 193 & 211 & 335 \\
$C$ & ???$\rightarrow$??? & 94 & 131 & 171 & 193 & 211 & 335 \\
$\alpha$ & ???$\rightarrow$??? & 94 & 131 & 171 & 193 & 211 & 335 \\
$\log_{10}(\beta)$ & ???$\rightarrow$??? & 94 & 131 & 171 & 193 & 211 & 335 \\
$\log_{10}(\delta)$ & ???$\rightarrow$??? & 94 & 131 & 171 & 193 & 211 & 335 \\
\enddata
%% Text for table notes should follow after the \enddata but before
%% the \end{deluxetable}. Make sure there is at least one \tablenotemark
%% in the table for each \tablenotetext.
